Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-03-01 src/article.tex
Non-restrictive clause in introduction

  \paragraph*{Methods:} The software outlined here ``Scaffolder'' is
  implemented in the Ruby programming language and can be installed via the
  RubyGems software management system. Genome scaffolds are defined using
  YAML - a markup language, which is both human and machine-readable. Command
  line binaries and extensive documentation are available.

>>>>

  \paragraph*{Methods:} The software outlined here, ``Scaffolder'', is
  implemented in the Ruby programming language and can be installed via the
  RubyGems software management system. Genome scaffolds are defined using YAML
  - a markup language, which is both human and machine-readable. Command line
  binaries and extensive documentation are available.
